The Eclipse Integrated Computational Environment

### 2019-07-31 src/content.tex
Addressed spelling errors.
Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

Local and remote jobs are often monitored to ascertain a job's status.
This monitoring could be a simple check as to whether or not the execution
has completed, or it could involve monitoring the output of individual
quantities to examine the calculation state. The latter is often used to
detect calculation errors that will result in incorrect results. If such
problems are found, the job is typically cancelled (``killed'') to save
compute resources and is then re-run later.

@@

In this work, it should be assumed---unless otherwise noted---that
``executing a job'' includes monitoring that job in one or more ways,
possibly including real-time updates to visualizations. It is also important to
note that executing a job is not the same as executing a workflow. Executing
jobs specifically refers to launching simulations, whereas executing a workflow
could be something different such as generating input or postprocessing
results. This is an important distinction because ICE's workflows are all
executed locally, but simulations and work can be distributed remotely
depending on the implementation of the workflow plugin.

\textbf{Analyzing results} includes executing special jobs to transform
data in one or more prescribed ways and producing artifacts with
scientific significance from the transformed data. This could include, for
example, postprocessing results and visualizing the new data with
dedicated visualization tools. For many types of scientific computing,
this includes viewing the results of a simulation on a mesh or grid and
extracting publication-quality images or movies from that data. Other
cases might include analyzing results in preparation for follow-on
simulations or performing feature extraction, classification, or
activities for machine learning and data mining.

@@

Solid-state sintering of parts printed using binder jetting
significantly increases part strength by decreasing the part porosity
and eliminating voids. However, this process does cause the resulting
product to shrink and warp from its original layout. An ideal near-net-shape 
process would combine binder jetting with solid-state sintering and account
for warpage and deformation in the part's design phase. 
Figure \ref{binder} shows an ICE-based workbench for performing simulations of
this process with visualizations of the pre- and postsimulation
properties of a central body with eight cantilevers. The primary
deformation in this type of geometry is bending or drooping of the
cantilevers due to sintering and thermal creep.

>>>>

Local and remote jobs are often monitored to ascertain a job's status.
This monitoring could be a simple check as to whether or not the execution
has completed, or it could involve monitoring the output of individual
quantities to examine the calculation state. The latter is often used to
detect calculation errors that will result in incorrect results. If such
problems are found, the job is typically canceled (``killed'') to save
compute resources and is then re-run later.

@@

In this work, it should be assumed---unless otherwise noted---that
``executing a job'' includes monitoring that job in one or more ways,
possibly including real-time updates to visualizations. It is also important to
note that executing a job is not the same as executing a workflow. Executing
jobs specifically refers to launching simulations, whereas executing a workflow
could be something different such as generating input or post-processing
results. This is an important distinction because ICE's workflows are all
executed locally, but simulations and work can be distributed remotely
depending on the implementation of the workflow plugin.

\textbf{Analyzing results} includes executing special jobs to transform
data in one or more prescribed ways and producing artifacts with
scientific significance from the transformed data. This could include, for
example, post-processing results and visualizing the new data with
dedicated visualization tools. For many types of scientific computing,
this includes viewing the results of a simulation on a mesh or grid and
extracting publication-quality images or movies from that data. Other
cases might include analyzing results in preparation for follow-on
simulations or performing feature extraction, classification, or
activities for machine learning and data mining.

@@

Solid-state sintering of parts printed using binder jetting
significantly increases part strength by decreasing the part porosity
and eliminating voids. However, this process does cause the resulting
product to shrink and warp from its original layout. An ideal near-net-shape 
process would combine binder jetting with solid-state sintering and account
for warpage and deformation in the part's design phase. 
Figure \ref{binder} shows an ICE-based workbench for performing simulations of
this process with visualizations of the pre- and post-simulation
properties of a central body with eight cantilevers. The primary
deformation in this type of geometry is bending or drooping of the
cantilevers due to sintering and thermal creep.
